Quality-of-Content (QoC)-Based Wireless Video Transmissions: A Joint Source Coding and APP-FEC Rate Allocation Scheme for Human Detections in Mobile Surveillance Networks

### 2015-07-23 draft.tex
test commit
Updated the MSE optimization equation, added one more symbol in the symbol list.

\textit{Notations:} The list of symbols used in this paper is summarized in Table \ref{Table: notations}.
\begin{table}[t]
\renewcommand{\arraystretch}{1.3}
\caption{List of symbols}
%\vspace{-.2in}
\begin{center}
\begin{tabular}{|p{0.45 in}|p{2.5 in}|}
\hline
\textbf{Symbol} & \textbf{Definition}  \\
\hline
$q$ & \text{Quantization parameter (QP)} \\ \hline
$P\left(\cdot\right)$ & Human detection accuracy model \\ \hline
$n$ & Application layer forward error correction (APP-FEC) block size \\ \hline
$k$ & Number of source packets in an APP-FEC block \\ \hline
$t$ & Correction capability of an APP-FEC block \\ \hline
$\epsilon$ & Reception overhead efficiency of APP-FEC \\ \hline
$p$ & Probability of packet loss \\ \hline
$f\left(\cdot\right)$ & APP-FEC block correction rate \\ \hline
$\Phi\left(\cdot\right)$ & Cumulative distribution function of the standard Gaussian distribution \\ \hline
$M$ & Total number of mobile nodes in the system \\ \hline
$T^{\left(\text{GoP}\right)}$ & Group of pictures (GoP) time period \\
$S$ & Packet size \\ \hline
$N_m$ & Number of detected people in the view of the mobile node $m$ \\ \hline
$R^{\left(\text{T}\right)}$ & Total data rate target of the system \\ \hline
$R^{\left(\min\right)}$ & Minimum data rate requirement of each mobile node \\ \hline
$\mathbb{N}$ & Set of nature numbers \\ \hline
$c_m^{\left(1\right)}, c_m^{\left(2\right)}$ & Parameters in QP-rate model of the mobile node $m$ \\ \hline
$r_m^{\left(\text{S}\right)}$ & Source coding rate target of the mobile node $m$ \\ \hline
$r_m^{\left(\text{B}\right)}$ & Transmission data rate target of the mobile node $m$ \\ \hline
$c_m^{\left(3\right)}$, $c_m^{\left(4\right)}$ & Parameters in a rate-distortion model of the MSE-driven rate allocation scheme in the control group. \\ \hline
$d_m\left(\cdot\right)$ & Distortion measured by the MSE in a rate-distortion model of the MSE-driven rate allocation scheme in the control group. \\

@@

Table \ref{Table: schemes} summarizes the proposed and other rate allocation schemes in the control group. We compare the proposed scheme with other three schemes. The first one is driven by video distortion measured by the mean-squared-error (MSE). We adopte a rate-distortion model in \cite{HOSC10} as:
\begin{equation}
d_m\left(r\right)=c_m^{\left(3\right)}r^{c_m^{\left(4\right)}},
\end{equation}
where $d_m\left(r\right)$ is the distortion in terms of MSE for the mobile node $m$. $c_m^{\left(3\right)}$ and $c_m^{\left(4\right)}$ are two parameters to be determined by curve-fitting. The MSE-driven rate allocation problem is expressed as:
\begin{equation}
\begin{array}{rl}
\min_{\mathbf{r}} &\sum_{m=1}^{M}d_m\left(r\right) \\
\text{subject to} & \sum\limits_{m=1}^{M}r_m\leq R^{\left(\text{T}\right)}\\
& r_m \geq R^{\left(\min\right)}, \forall m.
\end{array}
\end{equation}
The minimum data rate requirement $R^{\left(\min\right)}$ in our proposed scheme and the MSE-driven rate allocation scheme are both set as $200$ Kbps.

>>>>

\textit{Notations:} The list of symbols used in this paper is summarized in Table \ref{Table: notations}.
\begin{table}[t]
\renewcommand{\arraystretch}{1.3}
\caption{List of symbols}
%\vspace{-.2in}
\begin{center}
\begin{tabular}{|p{0.45 in}|p{2.5 in}|}
\hline
\textbf{Symbol} & \textbf{Definition}  \\
\hline
$q$ & \text{Quantization parameter (QP)} \\ \hline
$P\left(\cdot\right)$ & Human detection accuracy model \\ \hline
$n$ & Application layer forward error correction (APP-FEC) block size \\ \hline
$k$ & Number of source packets in an APP-FEC block \\ \hline
$t$ & Correction capability of an APP-FEC block \\ \hline
$\epsilon$ & Reception overhead efficiency of APP-FEC \\ \hline
$p$ & Probability of packet loss \\ \hline
$f\left(\cdot\right)$ & APP-FEC block correction rate \\ \hline
$\Phi\left(\cdot\right)$ & Cumulative distribution function of the standard Gaussian distribution \\ \hline
$M$ & Total number of mobile nodes in the system \\ \hline
$T^{\left(\text{GoP}\right)}$ & Group of pictures (GoP) time period \\
$S$ & Packet size \\ \hline
$N_m$ & Number of detected people in the view of the mobile node $m$ \\ \hline
$R^{\left(\text{T}\right)}$ & Total data rate target of the system \\ \hline
$R^{\left(\min\right)}$ & Minimum data rate requirement of each mobile node \\ \hline
$\mathbb{N}$ & Set of nature numbers \\ \hline
$c_m^{\left(1\right)}, c_m^{\left(2\right)}$ & Parameters in QP-rate model of the mobile node $m$ \\ \hline
$r_m^{\left(\text{S}\right)}$ & Source coding rate target of the mobile node $m$ \\ \hline
$r_m^{\left(\text{B}\right)}$ & Transmission data rate target of the mobile node $m$ \\ \hline
$c_m^{\left(3\right)}$, $c_m^{\left(4\right)}$ & Parameters in a rate-distortion model of the MSE-driven rate allocation scheme in the control group. \\ \hline
$d_m\left(\cdot\right)$ & Distortion measured by the MSE in a rate-distortion model of the MSE-driven rate allocation scheme in the control group. \\ \hline
$P^{\left(\text{req}\right)}$ & FEC block correction rate requirement of the MSE-driven rate allocation scheme in the control group. \\

@@

Table \ref{Table: schemes} summarizes the proposed and other rate allocation schemes in the control group. We compare the proposed scheme with other three schemes. The first one is driven by video distortion measured by the mean-squared-error (MSE). We adopte a rate-distortion model in \cite{HOSC10} as:
\begin{equation}
d_m\left(r\right)=c_m^{\left(3\right)}r^{c_m^{\left(4\right)}},
\end{equation}
where $d_m\left(r\right)$ is the distortion in terms of MSE for the mobile node $m$. $c_m^{\left(3\right)}$ and $c_m^{\left(4\right)}$ are two parameters to be determined by curve-fitting. The MSE-driven rate allocation problem is expressed as:
\begin{equation}
\begin{array}{rl}
\min_{\mathbf{\tilde{k}},\mathbf{\tilde{n}}} &\sum_{m=1}^{M}d_m\left(\frac{\tilde{k}^2_m \cdot S}{T^{\left(\text{GoP}\right)}}\right) \\
\text{subject to} & \sum\limits_{m=1}^{M}\tilde{n}^2_m\leq \frac{R^{\left(\text{T}\right)}T^{\left(\text{GoP}\right)}}{S}\\
& \tilde{k}_m \geq \sqrt{\frac{R^{\left(\min\right)}T^{\left(\text{GoP}\right)}}{S}}, \forall m, \\
& \tilde{n}_m \geq \tilde{k}_m, \forall m \\
& \log\Phi\left(\frac{\tilde{n}_m\left(1-p_m\right)-\frac{\tilde{k}_m^2}{\tilde{n}_m}}{\sqrt{p_m\left(1-p_m\right)}}\right) \geq \log(P^{\left(\text{req}\right)}), \forall m,
\end{array}
\end{equation}
where $P^{\left(\text{req}\right)}$ is a pre-defined BCR requirement, which is set as $0.99$ \cite{WSHZ13} in this paper. The minimum data rate requirement $R^{\left(\min\right)}$ in our proposed scheme and the MSE-driven rate allocation scheme are both set as $200$ Kbps.
